Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation

### 2023-03-20 beap_pres_dec2022/beap_pres_dec.tex
Updates to ppt presentation

	\begin{frame}{What Did we Do in this Study?}
		\begin{itemize}
			\item Programmed an ABC-MCMC using \texttt{C++} which consisted of a simulation step where amino acid sequences were altered by point mutations and insertions/deletions \newline
			\item Utilized the exponential distribution with ($\beta$ = length*indel\_rate) to see if the length of a repeat plays a role in its mutation \newline
			\item Attempted to estimate evolutionary parameters such as mutation rates and insertion/deletion rates \newline
			\item Explored summary statistics that could quantitatively explain characteristics of LCRs

@@

		\begin{enumerate}
			\item Propose a move from $\theta$ to $\theta'$ according to the normal distribution \pause
			\item Create a random protein sequence and mutate over many generations using $\theta'$ to generate simulated Dataset $D'$ \pause
			\item Calculate summary statistics for simulated dataset $D'$ \pause
			\item If $d(S',S) \le \epsilon$, go to next step, otherwise stay at $\theta$ and return to 1 \pause
			\item Accept $\theta'$ \pause
			\item Return to step 1
		\end{enumerate}

@@

	%Slide 14 - Maybe to this slide - Maybe throw in extra slides for reference
	%\begin{frame}{Simulation Step - MAYBE}

	%For my Results slides, I will talk about things such as the results I have, But i don't have any right now
	%SLIDE 15%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%\section{Results}
	%\begin{frame}{Results}

>>>>

	\begin{frame}{What Did we Do in this Study?}
		\begin{itemize}
			\item Programmed an ABC-MCMC using \texttt{C++} which consisted of a simulation step where amino acid sequences were altered by point mutations and insertions/deletions \newline
			\item Utilized the exponential distribution with ($\beta$ = length*indel\_rate) to examine if the length of a repeat plays a role in its mutation \newline
			\item Attempted to estimate evolutionary parameters such as mutation rates and insertion/deletion rates \newline
			\item Explored summary statistics that could quantitatively explain characteristics of LCRs

@@

		\begin{enumerate}
			\item Propose a move from $\theta$ to $\theta'$ according to the normal distribution $N(0.0,1.0)$
			\item Create and mutate a random protein sequence using $\theta'$ to generate the simulated Dataset $D'$ - do this 1000 times per newly proposed parameter value.
			\item Calculate summary statistics for simulated dataset $D'$ (average of all 1000 vectors of summary statistics)
			\item If $d(S',S) < previous\_distance$, go to next step, otherwise employ a one-sample t-test to assess the probability of accepting a larger distance. If the newly proposed distance is close to the previous distance, there is a higher chance we accept the value, otherwise we reject.
			\item Accept $\theta'$ 
			\item Return to step 1
		\end{enumerate}

@@

	%Slide 14 - Maybe to this slide - Maybe throw in extra slides for reference
	\begin{frame}{Simulation Step}
		\begin{center}
			\begin{enumerate}
			\item Random Protein Sequence \newline	
			GGAGGGAQ \newline		
			mutation rate = 0.14
			\qquad exp($\beta$), where $\beta$ = mutation rate\newline 
			indel rate = 0.14 \qquad exp($\beta$), where $\beta$ = length of repeat * indel rate \newline \pause

			\item Assign Exponential Deviates \newline
			mutation deviates = (0.83, 1.82, 2.35, 0.54, 0.98, 0.76, 1.53, 2.34) \newline
			indel deviates = (0.21, 1.21, 1.49, 0.86, 0.97, 1.13, 0.53, 0.35) \newline \pause

			\item Point Mutation, Insertion, or Deletion \newline
			Lowest value deviate = Residue that mutates fastest \newline \pause

			\item Upon point mutation, insertion, or deletion, scan the sequence again to see if the landscape of the sequence was affected, assign new deviates to affected amino acids only.

			\end{enumerate}
		\end{center}

	%For my Results slides, I will talk about things such as the results I have, But i don't have any right now
	%SLIDE 15%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Results}
	\begin{frame}{Results}
